Composable Algebra with Dependencies

### 2015-04-17 dAlg/mrm.tex
Up to MRM (extensibility)
Figures and citations

\usepackage{xcolor}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{doubleequals}
\usepackage{comment}
\usepackage{url}

@@

@@

@@

\bibliography{mrm}

>>>>

\usepackage{xcolor}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{doubleequals}
\usepackage{comment}
\usepackage{url}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\graphicspath{ {images/} }

@@

\input{sections/Scans}

\input{sections/FAlg}

@@

Apart from functors and F-Algebras, there are other ways to represent and evaluate
the DSL of parallel prefix circuits. In this section, we will show two other 
representations, and how they can be used to allow dependent interpretations.

@@

%\bibliography{mrm}

\begin{thebibliography}{}
\softraggedright

\bibitem{gibbons14}
  Gibbons, Jeremy and Wu, Nicolas.
  Folding Domain-Specific Languages: Deep and Shallow Embeddings.
  2014.

\bibitem{sheard04}
  Sheard, Tim and Pasalic, Emir.
  Two-level types and parameterized modules.
  \textit{Journal of Functional Programming}.
  14(5):547-587, September 2014.

\bibitem{fokkinga90}
  Fokkinga, Maarten M.
  Tupling and mutumorphisms.
  1990.

\bibitem{oliveira15}
  Oliveira, B.C.d.S., Mu, Shin-Cheng and You, Shu-Hung
  Modular Reifiable Matching: A List-of-Functors Approach to Two-Level Types
  February 2015.

\end{thebibliography}
